### 2017-11-28 manuscript.rmd
Figure 3 now inserted from file.

```{r species_phylogram, echo=FALSE, comment=NA, warning=FALSE, fig.width=6.5, fig.height=7, fig.cap="Phylogram of siphonophore relationships. Node labels indicate bootstrap support percent, unnumbered nodes have 100% support. The image was rendered with ggtree [@Yu:2016fo]" }

@@

	flip( p_phylogram, euphysonectae_node, calycophora_node )

@@

>>>>

```{r species_phylogram, echo=FALSE, comment=NA, warning=FALSE }

@@

	pdf("figures_for_AI/figure_3_raw.pdf")
	flip( p_phylogram, euphysonectae_node, calycophora_node )
	dev.off()

@@

![Phylogram of siphonophore relationships. Node labels indicate bootstrap support percent, unnumbered nodes have 100% support. The image was rendered with ggtree [@Yu:2016fo].](figures/Figure3.pdf)
